### 2014-01-21 inst/doc/README.Rmd
update installation instructions for suggested packages

```r
install_github("RHTMLForms", "omegahat")
install_github("XMLSchema", "omegahat")
```

>>>>

```r
# install_github("Sxslt", "omegahat")
# install_github("XMLSchema", "omegahat") 
# install_github("RHTMLForms", "omegahat")

install_github("RWordXML", "duncantl") # fails, clone and install locally

install.packages("Sxslt", repos="http://www.omegahat.org/R", type="source")
install.packages("RHTMLForms", repos="http://www.omegahat.org/R", type="source")
install.packages("XMLSchema", repos="http://www.omegahat.org/R", type="source")
